(f). (3 points) \textsl{The change in the network from Phase X to X+1 coincides with a major event that took place during the actual investigation. Identify the event and explain how the change in centrality rankings and visual patterns, observed in the network plots above, relates to said event. ($\sim$200 words, 300 word limit.)}\\

\textbf{Solution}:\\
The network plot shows the change from phase 4 to 5. It shows the behavior of the CAVIAR network on the first seizure of 300 kg of marijuana with a value of 2,500,000\$. The five most important nodes show an interesting effect of the seizure on the network (see table \ref{tab:centrality_phase_4_5}). In both phases node number 1 is by far the most important node. But the second node changes. In phase 4 no. 89 is the second most important node. But in phase 5 it is not even listed under the top five. Number 89 is the investor Antonio Iannacci.\\

\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline 
		 & Phase 4 & Phase 5 \\ 
		\hline 
		1st most important node & no. 1 (0.84) & no. 1 (0.88)  \\ 
		\hline 
		2nd most important node & no. 89 (0.20) & no. 12 (0.30) \\ 
		\hline 
		3rd most important node & no. 3 (0.09) & no. 83 (0.06) \\ 
		\hline 
		4th most important node & no. 83 (0.08) & no. 31 (0.06) \\ 
		\hline 
		5th most important node & no. 13 (0.06) & no. 85 (0.06) \\ 
		\hline 
	\end{tabular} 
	\caption{Change of centrality measures from phase 4 to 5 (node number and corresponding betweenness centrality)}
	\label{tab:centrality_phase_4_5}
\end{table}

In contrast node number 12 jumps on the second place in phase 5, even though it was not listed in the top five in phase 4. The seizure of marijuana seems to have a beneficial effect on the criminal career of Ernesto Morales, the principal organizer of the cocaine import and intermediary between the Colombians and the Serero organization. After this event cocaine is regularly seized in several phases.\\

The visualization of the networks shows graphically that besides node no. 1, node no. 12 emerges in the network. Node no. 89 is still represented, but is not as essential as before. There are several alternative connections for this node, in contrast to phase 4.\\